\maketitle
\abstract{ 
  In the \defn{cup game} two players, the \defn{filler} and the \defn{emptier},
  take turns adding and removing water from cups, subject to certain
  constraints. In the classic $p$-processor cup game the filler distributes
  $p$ units of water among the $n$ cups with at most $1$ unit of water to any
  particular cup, and the emptier chooses $p$ cups to remove at most one unit
  of water from. Analysis of the cup game is important for applications in
  processor scheduling, buffer management in networks, quality of service
  guarantees, and deamortization.

  We investigate a new variant of the classic $p$-processor cup game, which
  we call the \defn{variable-processor cup game}, in which the resources of the
  emptier and filler are variable. In particular, in the variable-processor cup
  game the filler is allowed to change $p$ at the beginning of each round. 
  Although the modification to allow variable resources seems small, we
  show that it drastically alters the game.

  We construct an adaptive filling strategy that achieves backlog
  $\Omega(n^{1-\varepsilon})$ for any constant $\varepsilon >0$ of our choice in
  running time $2^{O(\log^2 n)}$. This is enormous compared to the upper
  bound of $O(\log n)$ that holds in the classic $p$-processor cup game!
  We also present a simple adaptive filling strategy that is able to
  achieve backlog $\Omega(n)$ in extremely long games: it has running time
  $O(n!).$

  Furthermore, we demonstrate that this lower bound on backlog is tight: 
  using a novel set of invariants we prove that a greedy emptier never lets
  backlog exceed $O(n)$.

  We also construct an oblivious filling strategy that achieves backlog
  $\Omega(n^{1-\varepsilon})$ for $\varepsilon>0$ constant of our choice in time
  $2^{O(\log^2 n)}$ against any ``greedy-like" emptier with probability at least
  $1-2^{-\polylog(n)}$. Whereas classically randomization gives the emptier a
  large advantage, in the variable-processor cup game the lower bound is the same!
}
\thispagestyle{fancy} % page number to bottom right

