\documentclass[11pt]{article}
% \usepackage[subtle]{savetrees}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}

\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{hyperref}

\newtheorem{fact}{Fact}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{clm}{Claim}
\newtheorem{corollary}{Corollary}
\newtheorem{theorem}{Theorem}

\author{William Kuszmaul\textsuperscript{1}, Alek
Westover\textsuperscript{1}\\ 
\texttt{kuszmaul@mit.edu}, \texttt{alek.westover@gmail.com} }
\title{ An Adaptive Filling Strategy for achieving backlog
$\Omega(\log \frac{p}{n-p})$ \\ in the $p$-processor cup game on $n$ cups}
\date{\textsuperscript{1}Massachusetts Institute of Technology}

\begin{document}
\maketitle
\begin{abstract}
  The problem of scheduling tasks on $p$ processors so that no
  task ever gets too far behind is often described as a game with
  cups and water. In the $p$-processor cup game on $n$ cups,
  there are two players, a filler and an emptier, that take turns
  adding and removing water from a set of $n$ cups. In each turn,
  the filler adds $p$ units of water to the cups, placing at most
  $1$ unit of water in each cup, and then the emptier selects $p$
  cups to remove up to $1$ unit of water from; note that if a cup
  with fill less than $1$ is emptied from, its fill becomes $0$
  (not negative), and the average fill of the cups increases. The
  emptier's goal is to minimize the backlog, which is the height
  of the fullest cup.

  The $p$-processor cup game has been studied in many different
  settings, dating back to the late 1960's. Kuszmaul recently
  established that a greedy emptier never lets backlog exceed
  $O(\log n)$. Kuszmaul also gave a construction that achieves
  backlog $\Omega(\log (n-p))$. For small $p$, e.g. $p< n/2$, it
  is clear that $\Theta(\log n)$ is the optimal backlog, but for
  very large $p$ tight bounds are not known. 

  We give an adaptive filling strategy for the $p$-processor cup
  game on $n$ cups that achieves backlog $\Omega(\log
  \frac{p}{n-p})$. Combined with Kuszmaul's work, this implies
  that $\Theta(\log n)$ is the optimal backlog for the
  multi-processor cup game.
\end{abstract}

\section{Introduction}
The $p$-processor cup game on $n$ cups is a multi-round game
with two players, the \textbf{filler} and the \textbf{emptier},
that take turns adding and removing water from the cups. 
In particular, on each round the filler distributes $p$
units of fill arbitrarily amongst the cups, subject only to the
restriction that the filler cannot place more than $1$ unit of
fill into any given cup. Next, the emptier chooses $p$ cups and
removes at most $1$ unit of water from each of these.
The \textbf{backlog} is the height of the fullest cup; the emptier
aims to minimize backlog while the filler aims to maximize
backlog.

Kuszmaul showed that in the $p$-processor cup game on
$n$ cups the greedy emptying strategy---i.e. empty from the $p$
fullest cups---never lets backlog exceed $O(\log n)$. 
Kuszmaul also provided a filling strategy that achieves
backlog $\Omega(\log (n-p))$. 
For small $p$, e.g. $p \le n/2$, the upper-bound and lower-bound
match, but for large $p$ the bounds do not match. 

Many suspected that the $O(\log n)$ upper bound could be reduced
to $O(\log(n-p))$ even for large $p$; however, we show that this
is not the case.  

\section{Preliminaries}
Let $H_n = 1/1+1/2+\cdots +1/n$ denote the $n$-th harmonic
number. It is well known that $H_n = \Theta(\log n)$, and in fact
$H_n = \ln n + \Theta(1)$.

The \textbf{mass} of the cups is the sum the fills of all of the cups.

We remark that we consider only \textbf{adaptive} fillers, i.e. fillers
that can observe the state of the cups. The emptier can achieve
better bounds on backlog by using randomization, in which case
the emptier is not allowed to view the state of the cups, and is
called \textbf{oblivious}.

\section{Lower Bound on Backlog}
\begin{theorem}
  There is a filling strategy for the $p$-processor cup game on
  $n$ cups that achieves backlog $\Omega(\log n)$ against any emptier.
\end{theorem}
\begin{proof}
Kuszmaul's construction shows that there is a filling strategy
that achieves backlog $\Omega(\log (n-p))$.  If $p \le n -
\sqrt{n}$, then $n-p \ge \sqrt{n}$, so $\log (n-p) \ge
\frac{1}{2}\log (n)$, hence $\Omega(\log(n-p)) =
\Omega(\log(n))$. Thus the result holds for $p \le n - \sqrt{n}$;
we proceed to consider the case where $p > n-\sqrt{n}$.

We give a filling strategy, that we call \textbf{IncMass}, with
running time $O(p/(n-p))$, that increases the mass of the cups in
$n$ rounds by at least $1/2$, provided that backlog starts below
$O(\log n)$. The filler's strategy for achieving backlog
$\Omega(\log n)$ is to repeatedly use IncMass as many as
$\Theta(n\log n)$ times, terminating if backlog $\Omega(\log n)$
is ever achieved (after which the filler changes to the strategy
of placing a unit of water in the $p$ fullest cups on each
round). The filler's strategy either terminates before finishing,
which only happens if it has achieved backlog $\Omega(\log n)$,
or does not terminate early, in which case the mass of the cups
has increased by $\Omega(n\log n)$, implying that which means
that average fill and also backlog have increased by at least
$\Omega(\log n)$. We now describe IncMass.

Let $S$ denote the set of cups. The filler will maintain a set $U
\subset S$ throughout the algorithm. The algorithm's procedure
will ensure that once a cup enters $U$ its fill never decreases
for the rest of the process (by placing $1$ unit of water in such
a cup each round). Furthermore, $|U|$ will increase by $n-p$ at
each iteration of the process. $U$ is initialized to $\varnothing$.
For each of $\lfloor(p+1) / (n-p)\rfloor$ steps the filler will:
\begin{enumerate}
  \item Distribute $p - |U|$ water equally among the cups in
    $S\setminus U$ (thus, each such cup receives
    $\frac{p-|U|}{n-|U|}$ fill)
  \item Distribute $|U|$ water equally among the cups in $U$
    (thus, each such cup receives $1$ fill)
\end{enumerate}

Then the emptier must chose $p$ cups to empty from, and hence
$n-p$ cups to \textbf{neglect}, i.e. not empty from. Let $N$ be
the set of neglected cups on this step, with $|N| = n-p$. The
emptier adds all cups in $N \setminus U$ to $U$, and then
adds the $(n-p) - |N\setminus U |$ fullest cups in $S
\setminus U$ to $U$. 

The number of cups in $S\setminus U$ decreases by $n-p$ on of the
$\lfloor (p+1) / (n-p) \rfloor$ steps, so in the end we have
$|S\setminus U| \ge p+1$.

\begin{clm}
  Any cup $c \in S\setminus U$ at the end of this process has $0$
  fill, provided that the backlog started as at most $O(\log n)$.
\end{clm}
\begin{proof}
On the $i$-th step of the filler's process the fill of a
cup in $S \setminus U$ increases by $(p-|U|)/(n-|U|)$, and then
decreases by $1$ on this round, resulting in a net change of
$$-\frac{n-p}{n-(n-p)\cdot i}.$$
The total amount that the fill of $c$ has changed since
the start of the filler's process is simply the sum of the
amounts that the fill changes on each step, which is
\begin{equation}
  \label{eq:interesting}
\sum_{i=0}^{\big\lfloor \frac{p+1}{n-p}\big\rfloor - 1} \frac{n-p}{n-(n-p)\cdot i}.
\end{equation}
We aim to show that \eqref{eq:interesting} is $\Omega(\log n)$; combined
with the fact that the backlog started as $O(\log n)$ this will
imply that $c$ has fill $0$.

For $p=n-1$ \eqref{eq:interesting} is simply the difference of
harmonic numbers; this prompts the idea of lower bounding
\eqref{eq:interesting} by a difference of harmonic numbers.
We lower bound the $i$-th term in the sum by:
$$\frac{n-p}{n-i(n-p)} = \sum_{j=0}^{n-p-1} \frac{1}{n-i(n-p)} \ge \sum_{j=n-i(n-p)}^{n-(i-1)(n-p)-1}\frac{1}{j}.$$
Applying this to \eqref{eq:interesting} we get a difference of
harmonic numbers:
$${\sum_{i=0}^{\big\lfloor\frac{p+1}{n-p}\big\rfloor -
1}}\sum_{j=n-i(n-p)}^{n-(i-1)(n-p)-1} \frac{1}{j}.$$
This is now a difference of harmonic numbers. When $i=0,
j=n-(i-1)(n-p)-1$ we get the smallest term in the sum:
$$\frac{1}{n+(n-p-1)}.$$ 
When $i = \lfloor(p+1) / (n-p)\rfloor - 1, j=n-i(n-p)$ we get the largest
term in the sum, which is at least 
$$\frac{1}{n - \left(\frac{p+1}{n-p} -1\right) (n-p)} =
\frac{1}{2(n-p)-1}.$$
Thus, $c$ has lost fill at least 
$$H_{2n-p-1} - H_{2(n-p-1)} \ge \Omega\left(\log \frac{p}{n-p}\right).$$
Because $p > n-\sqrt{n}$ we have that $c$ has lost fill at least
$$\Omega\left(\log \frac{n-\sqrt{n}}{\sqrt{n}}\right) \ge
\Omega(\log n),$$
as desired. Because the backlog, and hence fill of $c$, started
less than $O(\log n)$ by assumption, $c$ must
now have $0$ fill.
\end{proof}

There are now (at least) $p+1$ cups with fill $0$. The final step
of the filler's procedure is to add $1/(p+1)$ fill to $p+1$ cups with
fill $0$. 
The emptier now must waste resources on emptying one of these
cups with fill below $1$. In total on this round the filler adds
$p$ units of fill to the cups, and then the emptier removes at
most $p-1 + 1/(p+1) \le p-1/2$ water to the cups. Hence the mass
increases by at least $1/2$. As mass is monotonically increasing,
this increase of $\frac{1}{2}$ in mass persists, as desired.

We have shown that IncMass can increase the mass given that
backlog starts below $O(\log n)$. As shown previously, by
repeatedly using IncMass we can achieve backlog $O(\log n)$.

We remark that the running time of IncMass is $O(p/(n-p))$ 
which satisfies
$$\sqrt{n} \le \frac{p}{n-p} \le n.$$
The running time of the full strategy is 
$$O\left(\frac{p}{n-p} n\log n\right) \le O(n^2 \log n).$$
\end{proof}

\section{Conclusion}
Our analysis shows that $\Theta(\log n)$ is a tight bound on
backlog in the $p$-processor cup game on $n$ cups with an
adaptive filler.

However, many open questions remain. The bounds on backlog in the
multi-processor cup game with an oblivious filler have \emph{not}
yet been made tight. In particular, there is a lower bound of
$\Omega(\log \log n)$, and an upper bound of $O(\log \log n +
\log p)$; for $p \le \log n$ the bounds are tight, but for large
$p$ they are not.

Further, analysis of the variant of the game where $p$ can
change, potentially with resource augmentation, is also of great
interest.

\end{document}
